---
title: "ESM262_Final"
author: "Claire Powers"
date: "6/5/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The goal of this assignment is to create a package that will be used for assessing climate change impacts and developing mitiation and adaptation strategies

(the goal here is to practice some coding skills so that routines and data may be provisional)

Here’s what the package should contain:  
- at least two different functions that summarize climate data in some way (your choice - it could be finding a trend, or finding extremes; or even simply mean winter precipitation)     

- at least two functions that calculate some measure of impact (you can really make these up) -so for example you could create a function that computes a heat stress index based on air temperature with parameters that vary for different species; or a function that estimates water supply from precipitation with parameters that vary to reflect water storage …you can make something up just as long as its somewhat sensible  
- one function that estimates the costs of impacts  
- use multi-dimensional arrays in one of your functions  

The package should contain:  
- some sample data  
- documentation for ALL functions  
- a vignette that shows how to use several of the functions with the sample data  
- 3 separate tests - (next weeks lecture)  

```{r clim_var_relationships}
library(tidyverse)
library(testthat)
clim_raw = read.table("clim.txt")

clim = clim_raw %>% 
  filter(year %in% 1980:2016) 

source("R/clim_regression.R")

climate_var_regress(clim,"tmin","month",plot = TRUE)


```


